Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-13 WSSSPE1_report/WSSSPE1_summary_report.tex
Section 3.2:  Keynote 2 refined a bit.

C. Titus Brown~\cite{ged-web}, a WSSSPE1 contributor and participant,
argued that with regard to reusable software, ``we should just start
doing it.'' Smith replied that documentation should be ``treated
as a first class entity.''  He noted that the open source community
has excellent cultures of code reuse, for example,
RubyGems~\cite{rubygems-web}, PyPI~\cite{pypi-web}, and
CPAN~\cite{cpan-web}, where there is effectively low-friction
collaboration through the use of repositories. This has not happened
in highly numerical, compiled language scientific software.  An
exception he cited as a good example of scientific projects using
GitHub is the EMCEE Markov Chain Monte Carlo project~\cite{emcee-web}
by Dan Foreman-Mackey and contributors.

>>>>

C. Titus Brown~\cite{ged-web}, a WSSSPE1 contributor and participant,
argued that with regard to reusable software, ``we should just start
doing it.'' In this regard Smith replied that documentation should be
``treated as a first class entity.''  He noted that the open source
community has excellent cultures of code reuse, for example,
RubyGems~\cite{rubygems-web}, PyPI~\cite{pypi-web}, and
CPAN~\cite{cpan-web}, where there is effectively low-friction
collaboration through the use of repositories. This has not happened
in highly numerical, compiled language scientific software.  An
exception he cited as a good example of scientific projects using
GitHub is the EMCEE Markov Chain Monte Carlo project~\cite{emcee-web}
by Dan Foreman-Mackey and contributors.
